Limit theorems for a class of critical superprocesses with stable branching

### 2019-05-30 presentation/stableLimit_beamer.tex
change stableLimit_beamer.tex sun190530

% ** Measure transform of superprocesses 
\subsection{Measure transform of superprocesses}
\begin{frame}{Methods/Measure transform of superprocesses}
\begin{block}{Theorem 3.}
  Let $\mu \in \mathcal M$ and write $\mathbb N_\mu(\cdot) := \int_{E} \mathbb N_x(\cdot)\mu(dx)$.
For each non-negative measurable function $F$ on $\mathbb D$ with $\mathbb N_\mu[F] \in (0,\infty)$, we have 
\begin{align}
\{(X_t)_{t\geq 0}; \mathbf P^{\mathcal N(F)}_\mu\} 
\overset{d}{=} \{(X_t)_{t\geq 0}; \mathbf P_\mu\} \otimes \{(w_t)_{t \geq 0}; \mathbb N^F_\mu(dw)\}.
\end{align}
\end{block}
    We can characterize $\{(w_t)_{t \geq 0}; \mathbb N^F_\mu(dw)\}$ while
    \begin{itemize}
    \item 
      $F(w) = w_t(\phi)$ using the {\color{red} classical Spine Decomposition Theorem}.
    \item 
      $F(w) = w_t(f)$ using a {\color{red} generalized Spine Decomposition Theorem}.
    \item 
      $F(w) = w_t(\phi)^2$ using a {\color{red} 2-Spine Decomposition Theorem.}
    \end{itemize}
\end{frame}

>>>>

% ** Measure transform of superprocesses 
\subsection{Measure transform of superprocesses}
\begin{frame}{Methods/Measure transform of superprocesses}
\begin{block}{Theorem 3.}
  Let $\mu \in \mathcal M$ and write $\mathbb N_\mu(\cdot) := \int_{E} \mathbb N_x(\cdot)\mu(dx)$.
For each non-negative measurable function $F$ on $\mathbb D$ with $\mathbb N_\mu[F] \in (0,\infty)$, we have 
\begin{align}
\{(X_t)_{t\geq 0}; \mathbf P^{\mathcal N(F)}_\mu\} 
\overset{d}{=} \{(X_t)_{t\geq 0}; \mathbf P_\mu\} \otimes \{(w_t)_{t \geq 0}; \mathbb N^F_\mu(dw)\}.
\end{align}
\end{block}
    We can characterize $\{(w_t)_{t \geq 0}; \mathbb N^F_\mu(dw)\}$ while
    \begin{itemize}
    \item 
      $F(w) = w_t(\phi)$ using the {\color{red} classical Spine Decomposition Theorem}.
    \item 
      $F(w) = w_t(f)$ using a {\color{red} generalized Spine Decomposition Theorem}.
    \item 
      $F(w) = w_t(\phi)^2$ using a {\color{red} 2-Spine Decomposition Theorem.}
    \end{itemize}
\end{frame}
% ** Size-biased add-on functions
\subsection{Size-biased add-on functions}

\begin{frame}{Methods/Size-biased add-on functions}
Recall that
\begin{align}
- \log E[e^{\theta \mathbf z^{(\gamma_0 - 1)}}] 
  \approx 1 -  E[e^{\theta \mathbf z^{(\gamma_0 - 1)}}] 
= \left( \frac{1}{1+\theta^{-(\gamma_0- 1)}} \right)^{\frac{1}{\gamma_0 - 1}}
\end{align}
\begin{block}{Lemma 2}
The non-linear delay equation 
 \begin{align}
{\color{blue} G(\theta) } 
= \int_0^\theta {\color{red}\exp\left\{ - \frac{\gamma_0}{\gamma_0 - 1} \int_0^1  G(ru^{\frac{1}{\gamma_0 - 1}})^{\gamma_0 - 1} \frac{du}{u} \right\} } dr,
\quad \theta \geq 0,
  \end{align}
has a unique solution:
\begin{align}
G(\theta) 
  = \left( \frac{1}{1+\theta^{-(\gamma_0- 1)}} \right)^{\frac{1}{\gamma_0 - 1}},
\quad \theta \geq 0. 
\end{align}
\end{block}

So the {\color{red} red part} can be considered as an approximation of the size-biased add-on functions of random variable $\mathbf z^{(\gamma_0 - 1)}$.
\end{frame}

\begin{frame}{Methods/Size-biased add-on functions}
  Recall that ${\color{blue} V_T(\theta f)(x)} = - \log \mathbf P_{\delta_x}[e^{- \theta X_T(f)}]$
  \begin{block}{Theorem 4.}
    For each non-negative bounded measurable function $f$, each $\theta \geq 0, x\in E$ and $T > 0$, we have
    \begin{align}
      &{\color{blue}V_T(\theta f)(x)} 
      \\&= \phi(x) \int_0^\theta {\color{Red} \Pi_{x}^{(\phi)} \left[ \frac{f(\xi_T)}{\phi(\xi_T)} \exp \left\{ - \int_0^T \left( \kappa \gamma V_{T - s}(rf)^{\gamma - 1} (\xi_s) \right) \right\}\right] } dr.
    \end{align}
  \end{block}
\begin{itemize}
\item
  The {\color{red} red} part is the size-biased add-on function of $X_T(f)$.
\item  
From Theorem 4 and Lemma 2, we can verify (details omitted) that
  \begin{align}
    \frac{V_t(\theta \eta_t f)(x)}{\eta_t \phi(x)} 
    \xrightarrow[t\to \infty]{} G(\theta),\quad \theta >0.
  \end{align}
\end{itemize}
\end{frame}
